Identifiers for Iterative Forecasting

### 2021-12-10 paper/paper.Rmd
support lmdb by path ending in lmdb

```{r}
db <- init_lmdb()
# FIXME should work with default methods
id <- register_lmdb("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542",
               db)
sources_lmdb(id, db)
```

@@

>>>>

```{r}
# LMDB is a database handle, not a path
db <- default_lmdb()
id <- register("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542",
               db)
sources(id, db)
```

@@

# Comparison to other approaches

Many other widely recognized software tools and techniques also rely on content-based identifiers, including, but limited to, IPFS, DAT, git, Torrents, and blockchains. ...
